Open-source landscape for 3D CSEM modelling

### 2020-04-16 manuscript/Manuscript.tex
small things

The continuous improvement of computing power and the CSEM boom in the early
2000's in the hydrocarbon industry led to a wealth of publications. The amount
of available numerical solutions can be overwhelming and is part of the reason
why there are hundreds of publications about the topic. There are the different
methods to solve Maxwell's equation, such as the IE method
\citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani,
CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the
differential equation (DE) method, for instance finite differences (FD)
\citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich,
CAG.13.Sommer}, finite elementes (FE) \citep{GJI.11.Schwarzbach, GEO.04.Commer,
GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, finite volume
(FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari}, and finite
integration technique (FIT) \citep{PIER.01.Clemens, GP.06.Mulder}. And these
are just the most common ones.

@@

\tabl[btp]{codecomparison}{All codes solve Maxwell's equations in its
  differential form (DE) under the quasistatic approximation. Note that
  \emg3d is a solver on its own, while the other codes implement third-package
  solvers such as \texttt{PETSc}, \texttt{MUMPS}, or \texttt{PARDISO}
  \citep{FGCS.04.Schenk}.
  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}
  \imycom[DW]{PEC/PMC instead of Dirichlet/Neumann?}
}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FIT & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & Neumann; Dirichlet & PEC & PEC & Dirichlet; Neumann \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

@@

\paragraph{Comments Raphael} “\emph{Yes, cutting the layers has an influce at
  offsets greater distance X (see example \#2 thesis) - depending on the
  boundary mesh. I'm sure that's the reason. I could also add a version with a
  way larger horizontal layered earth extent, but this would require way more
  resources - unstructured meshes are just not competitive to regular grids for
  regular geopmetries in such cases as discussed before}“

>>>>

The continuous improvement of computing power and the CSEM boom in the early
2000's in the hydrocarbon industry led to a wealth of publications. The amount
of available numerical solutions can be overwhelming and is part of the reason
why there are hundreds of publications about the topic. There are the different
methods to solve Maxwell's equation, such as the IE method
\citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani,
CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the
differential equation (DE) method, for instance finite differences (FD)
\citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich,
CAG.13.Sommer}, finite elementes (FE) \citep{GJI.11.Schwarzbach, GEO.04.Commer,
GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, finite volume
(FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari, PIER.01.Clemens,
GP.06.Mulder}. And these are just the most common ones.

@@

\tabl[btp]{codecomparison}{All codes solve Maxwell's equations in its
  differential form (DE) under the quasistatic approximation. Note that
  \emg3d is a solver on its own, while the other codes implement third-package
  solvers such as \texttt{PETSc}, \texttt{MUMPS}, or \texttt{PARDISO}
  \citep{FGCS.04.Schenk}.
  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}
  \imycom[DW]{PEC/PMC instead of Dirichlet/Neumann?}
}{
  \centering
  \footnotesize
\begin{tabularx}{\linewidth}{lXXXX}
  \toprule
  %
  & \custem & \emg3d & \petgem & \simpeg  \\
  \midrule
  %
  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
       & \href{https://empymod.github.io}{empymod.github.io}
       & \href{http://petgem.bsc.es}{petgem.bsc.es}
       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
  Installation & \texttt{pip}; \texttt{conda}
               & \texttt{pip}; \texttt{conda}
               & \texttt{conda}
               & \texttt{pip}; \texttt{conda} \\
  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
  Method & FE & FV & FE & FV \\
  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
  BC & Neumann; Dirichlet & PEC & PEC & Dirichlet; Neumann \\
  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
           \texttt{PARDISO}; \texttt{MUMPS} \\
  %
  \bottomrule
\end{tabularx}}%
%

@@

The difference becomes only significant at offsets larger than 8\,km. However,
this is due to a practical difference in the meshing: \textbf{Rewrite, Comments
Raphael} “\emph{Yes, cutting the layers has an influce at offsets greater
  distance X (see example \#2 thesis) - depending on the boundary mesh. I'm
  sure that's the reason. I could also add a version with a way larger
  horizontal layered earth extent, but this would require way more resources -
  unstructured meshes are just not competitive to regular grids for regular
geopmetries in such cases as discussed before}“

@@
